\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{geometry}
\geometry{margin=3cm}

\title{Control automation: Data engineering requirements}
\author{Author: Banele Mdluli}
\date{March 2026}

\begin{document}

\maketitle
\newpage
\begin{titlepage}
    \centering
    \vspace*{1cm}
    
    {\Huge\bfseries Version tracking\par}
    \vspace{2cm}
    
    % Add a table
    \begin{tabular}{|r|l|l|p{4cm}|l|}
        \hline
        \textbf{Version} & \textbf{Approvers} & \textbf{Approval status} & \textbf{Comments} &\textbf{Date} \\
        \hline
          1.0.0 & Banele Mdluli & Not required & compiling documentation & 12 March 2026\\
        \hline
    \end{tabular}
    
    \vfill
    
\end{titlepage}
\newpage

\section{Summary}
The project uses medallion architecture for data ingestion, processing and curation(consumption). The document will
contain a list of requirements for each layer of the architecture. The medallion architecture contains three layers
bronze, silver and gold. Bronze layer operations consist of pulling the data as is from an external storage source.
Silver layer operations are processes or methods used to convert the data formats to required formats. Additionally, 
enhance the data with audit fields and remove redundant fields. Gold layer operations are processess used to 
get the data ready for consumption by end-user or downstream systems.

\section{Data engineering requirements}
The requirements per each layer will apply to each table in that layer. Unless there are technical limitation that 
require additional or fewer requirements to be implemented.
\subsection{Raw layer requirements}
\begin{itemize}
    \item Copy the data AS-IS from the external source.
    \item (IF required) make changes that will enable the data to be save as delta tables
    \item Each table must stored in a catalog called raw\_control\_datalake.
    \item The table names must match the same names extracted from the external source.
    \item Include an ingestion datetime.
\end{itemize}
\subsection{Silver layer engineering requirements}
\begin{itemize}
    \item Extract the data from raw\_control\_datalake.
    \item Remove the \_id field and ingestion datetime field.
    \item Convert fields to become python friendly (USE snake format).
    \item Add ingestion datetime and modified datetime.
\end{itemize}
\subsection{Gold layer engineering requirements}
\begin{itemize}
    \item If a new table is created, then it should adhere silver layer requirements.
    \item If a table does not have primary key field, create a primary key that adheres to the rules.
\end{itemize}

\end{document}
